DeepAutoTrack (DAT): Vehicle Trajectory Prediction for Autonomous Driving

### 2018-01-26 paper/cvpr2018RebuttalKit/egrebuttal_3790.tex

\maketitle
\thispagestyle{empty}

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
We would first like to thank the reviewers for the supportive comments and the constructive criticisms. Your valuable feedbacks help us further improve the analysis and the overall presentation of the paper.
Because of the significant improvement made to the new version of the paper, we would kindly ask reviewers refer to the \href{https://www.jianguoyun.com/p/De5QypAQ9cyhBhjb10E}{new version of the paper}.
We address only the major criticisms below.
% and We would like to address the concerns respectfully as follows.

% Because of the space constraint we address only the major comments below.

\noindent \textbf{Modifications:} (1) We have implemented SocialLSTM [2] as requested by R2 and preliminary results on 2D space show that the inclusion of ``social interaction" further improves the prediction accuracy. (2) We have restructured our methodology in Sec. 3 and further explain the intuition behind the chosen architectures.

@@

%\noindent (3) We have rewritten and crystalized our contributions at the end of Sec. 1.

%\noindent \textbf{Common issues:}
%We would like to address the issues that are common to reviewers respectfully as follows:

\tcom
\noindent \textbf{R1: Unlike stated in the paper, vehicle tracking in images has been studied for years. There are summary papers (e.g. VEHICLE DETECTION AND TRACKING TECHNIQUES: A CONCISE REVIEW Raad Ahmed Hadi1,2 , Ghazali Sulong1 and Loay Edwar George, SIPIJ). There is no mention of prior art.}
\noindent \textbf{R1: There is no comparison to existing methods, the authors mention that this is due to the lack of existing datasets.}
\noindent \textbf{R2: Where are comparisons with other activity forecasting/trajectory prediction works?}

\noindent \textbf{Prior works on sequence prediction}:
We agree that the first version of the draft is indeed weak in presenting prior works on sequence prediction. We have restructured our related works. Specifically, we have supplemented prior works on activity forecasting/trajectory prediction in Sec 2.

@@

\tcom
\noindent \textbf{R1: It is not clear if the dataset is released with the paper.}
\noindent \textbf{R2: There is no comparison to existing methods, the authors mention that this is due to the lack of existing datasets.}
\noindent \textbf{R2: Who else has experimented on the SYNTHIA dataset? Or are the authors the first ones? Are the authors releasing a specific publicly-available prediction challenge based on SYNTHIA?}
\noindent \textbf{In the SocialLSTM paper Related Work section, there are about 20 sources that focus on Activity forecasting.}

\noindent \textbf{SYNTHIA and release of the dataset}:
\noindent Currently, experiments on the SYNTHIA dataset [27, 37] focus on single frame, static images for semantic labeling or scene representation. To our knowledge, our paper is the first attempt to utilize \emph{continuous video streams} for the prediction problem. We would like to release publicly-available dataset for prediction challenge based on SYNTHIA to spur future research upon paper publication.

\tcom
\noindent \textbf{R1: They adopt fDSST[6] and use it to track detections. What is the novelty, except for the implementation with specific parameters?}
\noindent \textbf{R2: I was a bit confused about why the tracking-by-detection” framework was novel -- how is it different from tracking-learning-detection” (TLD),from Z. Kalal, K. Mikolajczyk, and J. Matas. In TPAMI 2012?}
\noindent \textbf{R3: Figure 6: It would be nice to have some state-of-the-art tracking results as reference e.g. ECO, STAPLE CA, SiamFC}

\noindent \textbf{Instance association via tracking}:
\noindent  We would like to clarify the overloaded term ``tracking by detection" used in the first version of our manuscript. Most of the modern trackers focus on the problem of ``class-agnostic" generic object tracking\footnote{In order to adapt to temporal changes, a continuous learning strategy is applied, where the model is updated rigorously in every frame. This excessive update strategy causes both lower frame-rates and degradation of robustness due to model drifting caused by scale variations, deformations, and out-of-plane rotations.}.
In the context of autonomous driving, however, we know in advance the classes of object of interests for tracking (\emph{e.g.}, cars, pedestrians, cyclists). Therefore, with this extra source of information, we propose to use the neural nets object detection template to forcibly update the tacker's model to overcome the problem of model drifting. Hence the tracker is served solely as\emph{ instance associator}. During our qualitative examination, we find out that this combination achieves more robust result for instance association than using ``class-agnostic" tracker alone.

@@

% We would like to address the concerns respectfully as follows:
%####################################################################################################################################################################################
\tcom
\noindent \textbf{3) 3 very similar LSTMs with different input}
\noindent \textbf{4) The one LSTM with more information performs better. That is not surprising and not a real insight.}

\noindent \textbf{R1:} To our knowledge, our paper is the first attempt to take advantage of different level of abstractions from multiple streams to tackle the trajectory predictions with the practical use-case in mind (e.g. reaction time of humans). The limit of FtF temporal model shares the similarity mentioned in [4]: sampling frame by frame conditioned on the state and the previous correct token with an \textless EOS\textgreater token as a prerequisite.
We stipulate the length of the prediction fixed as T. Hence we have the assumption that current state is complete (Markovian), in the sense it contains all historical information required for predicting the future trajectory and the experimental results verify our intuition. 
Hence, we believe our paper serves as a good proof-of-concept and opens the doors for this challenging yet practical trajectory problem in the context of autonomous driving.

@@

%####################################################################################################################################################################################
\tcom
\noindent \textbf{Line 124 - The authors discuss a "lack of proper metrics for evaluating the temporal prediction result." How are the current metrics poorly suited to the task? What would be better?}

\noindent \textbf{R2:} Our preliminary result using 2D information shows that social tensor generates slightly better prediction than the isolation case (Tab.4, Fig.7, bottom row). Note that our mean error in unit space is much lower than the pedestrian trajectory prediction in Social-LSTM[2] (0.049 vs. 0.27). We analyze the following two factors:  car trajectory is a simpler case: both in time (prediction frame is 8 in our case and 12 in [2]) and in space (car trajectory is more linear and confined in our problem setting).
However, the relevant improvement using social tensor is lower for the car trajectory prediction (4\% vs. 38\%). We reckon it's due to  only around 3 cars of interests on average appearing in our high-way driving scenario.
And we believe in a more complex social scene such as urban driving, the improvement will be more pronounced.

### 2018-01-26 paper/cvpr2018/cvpr2018_3790.tex
Final version pdf

\noindent \textbf{Instance association} Instance association between frames is a prerequisite to solve the proposed intrinsically temporal problems.  3D scene flow is estimated in~\cite{behl2017bounding} by exploiting recognition to overcome the challenging scenarios in the presence of large displacement or local ambiguities.
%Their method achieve state-of-the-art performance on the KITTI2015 scene flow benchmark.
However, a total runtime of 10 minutes per frame is computationally prohibitive for the real-time deployment.
To accomplish the task of instance association between frames, we resort to the well studied field of visual tracking.
Discriminative Correlation Filters (DCF)~\cite{henriques2015high} have demonstrated excellent performance for high-speed generic visual object tracking.
Built upon their seminal work, there has been a plethora of recent improvements~\cite{hong2015online, ma2015hierarchical,danelljan2016beyond,held2016learning, wu2017kernalised,danelljan2017eco} relying on convolutional neural network (CNN) pretrained on ImageNet as a feature extractor for visual tracking.

Most of the modern trackers focus on the problem of ``class-agnostic" generic object tracking. In order to adapt to temporal changes, a continuous learning strategy is applied, where the model is updated rigorously in every frame. Such update is excessive and sensitive to sudden changed caused by, \emph{e.g.}, scale variations, deformations, and out-of-plane rotations. This excessive update strategy cause both lower frame-rates and degradation of robustness due to over-fitting to the recent frames~\cite{danelljan2017eco}.
In the context of autonomous driving, however, we know in advance the classes of object of interests for tracking (\emph{e.g.}, cars, pedestrians, cyclists). Therefore, with this extra source of information, we propose to use the neural nets object detection result as a more robust template to update the tacker's model to overcome the problem of model drifting. Hence the tracker is served solely as instance associator for the traffic participant.

\begin{figure*}[t]
        \centering
        \includegraphics[width=0.90\textwidth]{figures/framework.pdf}
        \caption{
        \small{The framework for the proposed vehicle future trajectory prediction system. The input is the sequential data (RGB and/or depth maps) up to the current time step obtained from the host car. Target vehicles' sequential bounding boxes are extracted by detection \& tracking module. Along with scene semantics as an auxiliary information, multi-stream inputs are fed into an LSTM to predict future trajectories taking advantages of various levels of abstractions.}
        }
        \label{fig:framework}
\end{figure*}
%\noindent \textbf{RNN for sequence prediction}

@@

More recent works also attempt to take the ``social factor" into consideration. Social-LSTM~\cite{alahi2016social} focus on modeling dynamics crowd interactions for path prediction by introducing a ``social tensor" from a spatial-temporal neighborhood. Based on the social-LSTM, an attention mechanism is introduced in ~\cite{social_lstm_2018} built upon the high-level spatio-temporal graphs proposed in~\cite{jain2016structural}.
%~\cite{duself} used 3D convolutional layers to extract visual features, then fed them into LSTM layers to capture the sequential relation. In addition to using deep features, ~\cite{koutnik2013evolving} trained a large recurrent neural network using a reinforcement learning approach to map images directly to steering angles, with the purpose to keep the car on track.

@@

\subsection{Problem formulation}
\begin{figure}[t]
        \centering
        \includegraphics[width=0.45\textwidth]{figures/network_detail.pdf}
        \caption{
        \small{Illustrations of three temporal networks. $\mathcal{J_H}$ represents historical trajectories, $\mathcal{J_F}$ is the $T$ time step future trajectories to be predicted.  Left: Frame-to-Frame (FtF); Middle: Frame-to-Sequence (FtS); Right: SEG-LSTM, with auxiliary information as input $\mathcal{A}$. The social tensor $\mathcal{S}$ can be inserted into existing recurrent networks .}
        }
        \label{fig:lstm}
\end{figure}

We propose to learn a generic approach from history information and formulate the problem as predicting future traffic participants' trajectories.
%Our work is most related to~\cite{xu2017end} where their problem was to predict future (next 1/3rd second) feasible actions of egomotion from a motion reflex perspective.
%We, instead,  predict other traffic participants' future trajectories in a longer time span (next 1.6 second).
Formally, our problem can be defined as a mapping $\mathcal{M}$ between historical trajectory $\mathcal{J_H}=\{j_p^t\}, t=1,\dots, T $ with auxiliary information $ \mathcal{A}=\{a_p^t\},t=1,\dots, T $ for traffic participant $p$ and the future trajectory $\mathcal{J_F}=\{j_p^t\}, t={T+1}, \ldots, T_F$:

@@

%Auxiliary information $\mathcal{A}$ could be scene semantics to regularize the path of future trajectory or car pose information to decide whether it's an approaching car or a parallel driving car.

\begin{figure}[t]
        \centering
        \includegraphics[width=0.42\textwidth]{figures/SEGLSTM.pdf}
        \caption{
        \small{Diagram of SEG-LSTM model: semantic inputs are one-hot encoded images with channel number $\mathcal{C}$ as the number of semantic categories (we used only ``car" and ``road" as the two semantics used under the context of high-way driving). The higher level semantics are extracted through a four-layer CNN, producing a joint representation of the auxiliary semantic information and the co-ordinate trajectory information.}
        }
        \label{fig:SEGLSTM}
\end{figure}
\subsection{Sequence modeling}

For predicting the vehicle's future trajectory, we compare three temporal models based on LSTM cells. A ``social pooling tensor" that implicitly reasons about the motion of neighboring traffic participants can be inserted into existing recurrent network architectures without any extra training supervision or modification to the optimization process as shown in Fig.~\ref{fig:lstm}. The first two models take sequential 3D occupancy as input. In the third model, we  explore using semantic segmentation as a side ``auxiliary" information $\mathcal{A}$ to better guide the trajectory prediction.

\vspace{\baselineskip}
\noindent \textbf{Frame-to-Frame (FtF) model:}
is akin to  sequence generation model from Graves~\cite{graves2013generating}.  At test-time $t$, it samples current predicted 3D occupancy as feedback to the model for predicting next frame occupancy grid. The model is frame to frame Markovian and the next frame trajectory $j_{t+1}$ can be estimated as:
\begin{equation}
j_{t+1} \leftarrow  \bm{\mathcal{M}}(j_t, j_H): \mathcal{J_H}
\label{eq:FtF}
\end{equation}

@@

\vspace{\baselineskip}
\noindent \textbf{SEG-LSTM model:}
 takes advantages of scene semantics from  historical frames as auxiliary information $\mathcal{A}$. The second LSTM layer fuses the output from the bottom-most LSTM that encodes co-ordinates embedding with higher level semantic information.
With auxiliary $\mathcal{A}$, the trajectory  $j_{t+1, \ldots, T_F}$  to be predicted can be estimated as:
\begin{equation}
j_{t+1, \ldots, T_F}, \leftarrow  \bm{\mathcal{M}}(j_H, a): \mathcal{J_H} \times convnet(\mathcal{A})
\label{eq:SEG-LSTM}
\end{equation}
 Semantic inputs are one-hot encoded images with channel number $\mathcal{C}$ as the number of semantic categories  as in Fig.~\ref{fig:SEGLSTM}. The higher level semantic is extracted through a four-layer CNN, producing a joint representation of the semantic auxiliary information and the co-ordinate trajectory information.
 As described above, the 3D occupancy input  has only six dimensions: $[x, y, w, h, d_{min}, d_{max}]$ encoding the co-ordinates information. So the bottom-most LSTM not only can learn the temporal information between time-varying trajectories,  but also can balance input dimensions of both co-ordinate information and the semantic information.
%Results show that the SEG-LSTM model performs better than the other two temporal model.

Note that this model differs from the way semantic information is used in~\cite{xu2017end}: instead of using semantic segmentation as a ``privilege information" which is missing at test time, SEG-LSTM directly takes historical scene semantics as input and directs the recurrent net future trajectory prediction.

\vspace{\baselineskip}
\noindent \textbf{Social tensor:} was firstly introduced in~\cite{alahi2016social} by observing the ``common sense" rules and social conventions from pedestrians in crowded public space. Naturally, in the context of autonomous driving, such observation is also complied: when there are multiple cars occupying on-going lanes, the social interactions between traffic participants confine the space for their possible trajectories. The social interactions can be encoded implicitly by using a social pooling layer: at every time-step, the LSTM cell receives pooled hidden-state information from the LSTM cells of neighbors. While pooling the information, the spatial information is preserved by grid based pooling. The hidden state $h^t_i$ of the LSTM at time $t$ captures the latent representation of the $i^{th}$ target in the scene. This representation can be shared with neighbors by building a social hidden tensor $s^i_t$:
\begin{equation}
s^i_t = \sum_{j \in \mathcal{N}_i} \mathbf{1}_{m,n} [x^j_t - x^i_t, y^j_t - y^i_t] \centerdot  h^j_{t-1}
\label{eq:social_tensor}
\end{equation}
where $\mathbf{1}_{m,n} [x^j_t - x^i_t, y^j_t - y^i_t]$ is an indicator function to check if $(x, y)$ is in the $(m, n)$ cell of the grid, and $\mathcal{N}_i$ is the set of neighbors corresponding to target $i$.
The trajectory  to be predicted can be estimated as:
\begin{equation}
j_{t+1, \ldots, T_F}, \leftarrow  \bm{\mathcal{M}}(j_H, s^i_H): \mathcal{J_H}  \times \mathcal{S}
\label{eq:FtS}
\end{equation}
This social pooling layer does not introduce any additional parameters and can be inserted in to the hidden layer of LSTM. An important distinction from the vanilla LSTM is that the hidden states of multiple LSTMs are coupled by the social pooling layer. At every time-step, the update are jointly back-propagated through multiple LSTMs in a scene as a neighboring batch update scheme.

@@

For the social tensor configuration, we incorporate all vehicles in the same time-step as their neighbors. In contrast with~\cite{alahi2016social} where a spatial constraint is required in order to be counted as a neighbor, all the vehicles in the same scene are relevant for the social interactions under our high-way driving context.
Grid size is set as 4 and the embedding size is 64 so the social tensor $\mathcal{S}$ is a $4\times 4\times 64$ matrix.
The learning is set to 0.001 and RMS-prop~\cite{tieleman2012lecture} with a gradient clipping of 3 to avoid divergence.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure*}[t]
%   \centering
%    \begin{subfigure}[c]{0.25\textwidth}
%    \centering
%    \includegraphics[width=7cm,height=5cm, clip]{figures/precision_plot_2d.png}
%    \caption{\small{Precision plot for 2D (pixel as x-axis)}}
%    \end{subfigure}%
%    \begin{subfigure}[c]{0.25\textwidth}
%    \centering
%        \includegraphics[width=7cm,height=5cm, clip]{figures/success_plot_2d.png}
%        \caption{\small{Success plot 2D ()}}
%    \end{subfigure}
%     \begin{subfigure}[c]{0.25\textwidth}
%     \includegraphics[width=7cm,height=5cm, clip]{figures/precision_plot_3d_20cm.png}
%    \caption{\small{Precision plot for 3D (centimeter as x-axis)}}
%    \end{subfigure}%
%    \begin{subfigure}[c]{0.25\textwidth}
%    \centering
%        \includegraphics[width=7cm,height=5cm, clip]{figures/success_plot_3d.png}
%        \caption{\small{Success plot 3D (IOU as x-axis)}}
%    \end{subfigure}
%\caption{\small{ 2D and 3D space precision plot and success plot.}}
%\label{fig:precision_plot_and_success_plot}
%\end{figure*}

@@

\begin{figure*}[t]
        \centering
        \includegraphics[width=0.95\textwidth]{figures/prediction_2.pdf}
        \caption{
        \small{Visualization of prediction results. Top two rows show the advantage of using semantics in temporal model: {\color{red}Red: ground truth}; {\color{blue}Blue: SEG-LSTM}; {\color{green}Green: FtS}; {\color{yellow}Yellow: FtF}.
        SEG-LSTM can help detecting neighboring vehicles and restricts the viable path outside the space occupied by other vehicles (row 1) and confines the plausible car trajectory along the space above road (row 2).
        Row 3 and 4 show the benefit  of incorporating social factors.
        Row 3 is the visualization for vanilla LSTM. The bottom left car prediction (denoted by red dots) is considered in isolation and could surpass the host car, moving dangerously close to the two front cars. Row 4 is the visualization of social LSTM: by considering two front cars in the scene, the predicted keeps the red dot car in a safer distance from two front cars.
        }
        }
        \label{fig:final}
\end{figure*}

@@

%%%%%%%%%%%%%%%%%
\begin{table}[t]
\small
   \centering
        %\begin{tabular}{|l *{2}{c}|}\hline
        %\begin{tabu}{|l *{2}{c}|}
        \begin{tabu}{@{}ccc@{}}\toprule
        [-1pt] \tabucline[1pt]{1-3}
                                                    &   Ave. disp. error      & Final disp. error   \\ \hline
            {\small Vanilla LSTM }                 &     0.0514              &  0.0880   \\
            {\small \textbf{Social LSTM} }         &  \textbf{0.0494 }         & \textbf{0.0837}   \\
          [-1pt] \tabucline[1pt]{1-3}
        \end{tabu}
        %\end{tabular}

    \caption{ {\small Results comparing vanilla LSTM and social LSTM in  unit space. \emph{Ave. disp. error} is the mean square error over all estimated points of a trajectory and the true points. \emph{Final disp. error} is the distance beween the predicted final destination and the true final destination at the end of the prediction period $T_F$.
     }
    } \label{tab:social_lstm}
\end{table}

%\vspace{\baselineskip}
\noindent \textbf{Learning with auxiliary information:}
 The 2D and 3D evaluation results in Fig.~\ref{fig:precision_plot_and_success_plot} and Tab.~\ref{table_baseline_2d}  show that our proposed system consistently outperforms the baseline Kalman filter. Kalman filter is intrinsically a linear model and it's difficult to handle highly nonlinear driving trajectories in a relative coordinate.
 The auxiliary learning with semantic information in SEG-LSTM also consistently outperforms other two temporal models.
 Fig.~\ref{fig:final} shows the advantage of using SEG-LSTM: by utilizing the scene semantics (\emph{e.g.}, road, cars), it's able to direct the recurrent net to output the most plausible path for vehicles and avoid collision with neighboring vehicles.

%\vspace{\baselineskip}
\noindent \textbf{Learning with social tensor:}
On average, there is around 3 cars of interests in a high-way driving scene.
Tab.~\ref{tab:social_lstm} shows that considering social interactions between cars improves the prediction accuracy than the isolation case.
And we believe that in a more complex social scene such as urban driving, the improvement will be more pronounced.

>>>>

\begin{figure*}[t]
        \centering
        \includegraphics[width=0.90\textwidth]{figures/framework.pdf}
        \caption{
        \small{The framework for the proposed vehicle future trajectory prediction system. The input is the sequential data (RGB and/or depth maps) up to the current time step obtained from the host car. Target vehicles' sequential bounding boxes are extracted by detection \& tracking module. Along with scene semantics as an auxiliary information, multi-stream inputs are fed into an LSTM to predict future trajectories taking advantages of various levels of abstractions.}
        }
        \label{fig:framework}
\end{figure*}
\noindent \textbf{Instance association} Instance association between frames is a prerequisite to solve the proposed intrinsically temporal problems.  3D scene flow is estimated in~\cite{behl2017bounding} by exploiting recognition to overcome the challenging scenarios in the presence of large displacement or local ambiguities.
%Their method achieve state-of-the-art performance on the KITTI2015 scene flow benchmark.
However, a total runtime of 10 minutes per frame is computationally prohibitive for the real-time deployment.
To accomplish the task of instance association between frames, we resort to the well studied field of visual tracking.
Discriminative Correlation Filters (DCF)~\cite{henriques2015high} have demonstrated excellent performance for high-speed generic visual object tracking.
Built upon their seminal work, there has been a plethora of recent improvements~\cite{hong2015online, ma2015hierarchical,danelljan2016beyond,held2016learning, wu2017kernalised,danelljan2017eco} relying on convolutional neural network (CNN) pretrained on ImageNet as a feature extractor for visual tracking.

Most of the modern trackers focus on the problem of ``class-agnostic" generic object tracking. In order to adapt to temporal changes, a continuous learning strategy is applied, where the model is updated rigorously in every frame. Such update is excessive and sensitive to sudden changed caused by, \emph{e.g.}, scale variations, deformations, and out-of-plane rotations. This excessive update strategy cause both lower frame-rates and degradation of robustness due to over-fitting to the recent frames~\cite{danelljan2017eco}.

%In the context of autonomous driving, however, we know in advance the classes of object of interests for tracking (\emph{e.g.}, cars, pedestrians, cyclists). Therefore, with this extra source of information, we propose to use the neural nets object detection result as a more robust template to update the tacker's model to overcome the problem of model drifting. Hence the tracker is served solely as instance associator for the traffic participant.

%\noindent \textbf{RNN for sequence prediction}

@@

More recent works also attempt to take the ``social factor" into consideration. Social-LSTM~\cite{alahi2016social} focus on modeling dynamics crowd interactions for path prediction by introducing a ``social tensor" from a spatial-temporal neighborhood. Based on the Social-LSTM, an attention mechanism is introduced in ~\cite{social_lstm_2018} built upon the high-level spatio-temporal graphs proposed in~\cite{jain2016structural}.
%~\cite{duself} used 3D convolutional layers to extract visual features, then fed them into LSTM layers to capture the sequential relation. In addition to using deep features, ~\cite{koutnik2013evolving} trained a large recurrent neural network using a reinforcement learning approach to map images directly to steering angles, with the purpose to keep the car on track.

@@

\subsection{Problem formulation}

We propose to learn a generic approach from history information and formulate the problem as predicting future traffic participants' trajectories.
%Our work is most related to~\cite{xu2017end} where their problem was to predict future (next 1/3rd second) feasible actions of egomotion from a motion reflex perspective.
%We, instead,  predict other traffic participants' future trajectories in a longer time span (next 1.6 second).
Formally, our problem can be defined as a mapping $\mathcal{M}$ from historical trajectory $\mathcal{J_H}=\{j_p^t\}, t=1,\dots, T $ with auxiliary information $ \mathcal{A}=\{a_p^t\},t=1,\dots, T $ for traffic participant $p$ to the future trajectory $\mathcal{J_F}=\{j_p^t\}, t={T+1}, \ldots, T_F$:

@@

%Auxiliary information $\mathcal{A}$ could be scene semantics to regularize the path of future trajectory or car pose information to decide whether it's an approaching car or a parallel driving car.
\begin{figure}[t]
        \centering
        \includegraphics[width=0.45\textwidth]{figures/network_detail.pdf}
        \caption{
        \small{Illustrations of three temporal networks. $\mathcal{J_H}$ represents historical trajectories, $\mathcal{J_F}$ is the $T$ time step future trajectories to be predicted.  Left: Frame-to-Frame (FtF); Middle: Frame-to-Sequence (FtS); Right: SEG-LSTM, with auxiliary information as input $\mathcal{A}$. The social tensor $\mathcal{S}$ can be inserted into existing recurrent networks .}
        }
        \label{fig:lstm}
\end{figure}

\subsection{Sequence modeling}

For predicting the vehicle's future trajectory, we compare three temporal models based on LSTM cells. A ``social pooling tensor" that implicitly reasons the motion of neighboring traffic participants can be inserted into existing recurrent network architectures without any extra training supervision or modification to the optimization process as shown in Fig.~\ref{fig:lstm}. The first two models take sequential 3D occupancy as input. In the third model, we  explore using semantic segmentation as a side ``auxiliary" information $\mathcal{A}$ to better guide the trajectory prediction.

\vspace{\baselineskip}
\noindent \textbf{Frame-to-Frame (FtF) model:}
is akin to  sequence generation model from Graves~\cite{graves2013generating}.  At test-time $t$, it samples current predicted 3D occupancy as feedback to the model for predicting next frame occupancy grid. The model is frame-to-frame Markovian and the next frame trajectory $j_{t+1}$ can be estimated as:
\begin{equation}
j_{t+1} \leftarrow  \bm{\mathcal{M}}(j_t, j_H): \mathcal{J_H}
\label{eq:FtF}
\end{equation}

@@

\begin{figure}[t]
        \centering
        \includegraphics[width=0.42\textwidth]{figures/SEGLSTM.pdf}
        \caption{
        \small{Diagram of SEG-LSTM model: semantic inputs are one-hot encoded images with channel number $\mathcal{C}$ as the number of semantic categories (we used only ``car" and ``road" as the two semantics  under the context of high-way driving). The higher level semantics are extracted through a four-layer CNN. A joint representation is produced by the auxiliary semantic information and the coordinates trajectory information.}
        }
        \label{fig:SEGLSTM}
\end{figure}
\vspace{\baselineskip}
\noindent \textbf{SEG-LSTM model:}
 takes advantages of scene semantics from  historical frames as auxiliary information $\mathcal{A}$. The second LSTM layer fuses the output from the bottom-most LSTM that encodes coordinates embedding with higher level semantic information.
With auxiliary $\mathcal{A}$, the trajectory  $j_{t+1, \ldots, T_F}$  to be predicted can be estimated as:
\begin{equation}
j_{t+1, \ldots, T_F}, \leftarrow  \bm{\mathcal{M}}(j_H, a): \mathcal{J_H} \times \mathcal{A}
\label{eq:SEG-LSTM}
\end{equation}
 Semantic inputs are one-hot encoded images with channel number $\mathcal{C}$ as the number of semantic categories  as in Fig.~\ref{fig:SEGLSTM}. The higher level semantic is extracted through a four-layer CNN. A joint representation is produced  by the semantic auxiliary information and the coordinates trajectory information.
 As described above, the 3D occupancy input  has only six dimensions: $[x, y, w, h, d_{min}, d_{max}]$ encoding the coordinates information. So the bottom-most LSTM not only can learn the temporal information between time-varying trajectories,  but also can balance input dimensions of both coordinates information and the semantic information.
%Results show that the SEG-LSTM model performs better than the other two temporal model.

Note that this model differs from the way semantic information is used in~\cite{xu2017end}: instead of using semantic segmentation as a ``privilege information" which is missing at test time, SEG-LSTM directly takes historical scene semantics as input and embeds them to a hidden-state tensor by a convolutional neural network.

\vspace{\baselineskip}
\noindent \textbf{Social tensor:} was firstly introduced in~\cite{alahi2016social} by observing the ``common sense" rules and social conventions from pedestrians in crowded public space. Naturally, in the context of autonomous driving, such observation is also complied: when there are multiple cars occupying on-going lanes, the social interactions between traffic participants confine the space for their possible trajectories. The social interactions can be encoded implicitly by using a social pooling layer: at every time-step, the LSTM cell receives pooled hidden-state information from the LSTM cells of neighbors. While pooling the information, the spatial information is preserved by grid based pooling.

The hidden state $h^t_i$ of the LSTM at time $t$ captures the latent representation of the $i^{th}$ target in the scene. This representation can be shared with neighbors by building a social hidden tensor $s^i_t$:
\begin{equation}
s^i_t = \sum_{j \in \mathcal{N}_i} \mathbf{1}_{m,n} [x^j_t - x^i_t, y^j_t - y^i_t] \centerdot  h^j_{t-1}
\label{eq:social_tensor}
\end{equation}
where $\mathbf{1}_{m,n} [x^j_t - x^i_t, y^j_t - y^i_t]$ is an indicator function to check if $(x, y)$ is in the $(m, n)$ cell of the grid, and $\mathcal{N}_i$ is the set of neighbors corresponding to target $i$.
The trajectory  to be predicted can be estimated as:
\begin{equation}
j_{t+1, \ldots, T_F}, \leftarrow  \bm{\mathcal{M}}(j_H, s^i_H): \mathcal{J_H}  \times \mathcal{S}
\label{eq:FtS}
\end{equation}
This social pooling layer does not introduce any additional parameters and can be inserted into the hidden layer of LSTM. An important distinction from the vanilla LSTM is that the hidden states of multiple LSTMs are coupled by the social pooling layer. At every time-step, the updates are jointly back-propagated through multiple LSTMs in a scene as a neighboring batch update scheme.

@@

For the social tensor configuration, we incorporate all vehicles in the same time-step as their neighbors. In contrast with~\cite{alahi2016social} where a spatial constraint is required in order to be counted as a neighbor, all the vehicles in the same scene are relevant for the social interactions under our high-way driving context.
Grid size is set as 4 and the embedding size is 64 so the social tensor $\mathcal{S}$ is a $4\times 4\times 64$ matrix.
The learning rate is set to 0.001 with RMS-prop~\cite{tieleman2012lecture} with a gradient clipping of 3 to avoid divergence.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure*}[t]
%   \centering
%    \begin{subfigure}[c]{0.25\textwidth}
%    \centering
%    \includegraphics[width=7cm,height=5cm, clip]{figures/precision_plot_2d.png}
%    \caption{\small{Precision plot for 2D (pixel as x-axis)}}
%    \end{subfigure}%
%    \begin{subfigure}[c]{0.25\textwidth}
%    \centering
%        \includegraphics[width=7cm,height=5cm, clip]{figures/success_plot_2d.png}
%        \caption{\small{Success plot 2D ()}}
%    \end{subfigure}
%     \begin{subfigure}[c]{0.25\textwidth}
%     \includegraphics[width=7cm,height=5cm, clip]{figures/precision_plot_3d_20cm.png}
%    \caption{\small{Precision plot for 3D (centimeter as x-axis)}}
%    \end{subfigure}%
%    \begin{subfigure}[c]{0.25\textwidth}
%    \centering
%        \includegraphics[width=7cm,height=5cm, clip]{figures/success_plot_3d.png}
%        \caption{\small{Success plot 3D (IOU as x-axis)}}
%    \end{subfigure}
%\caption{\small{ 2D and 3D space precision plot and success plot.}}
%\label{fig:precision_plot_and_success_plot}
%\end{figure*}

@@

\begin{figure*}[t]
        \centering
        \includegraphics[width=0.95\textwidth]{figures/prediction_2.pdf}
        \caption{
        \small{Visualization of prediction results. Top two rows show the advantage of using semantics in temporal model: {\color{red}Red: ground truth}; {\color{blue}Blue: SEG-LSTM}; {\color{green}Green: FtS}; {\color{yellow}Yellow: FtF}.
        SEG-LSTM can help detecting neighboring vehicles and restrict the viable path outside the space occupied by other vehicles (row 1); and confine the plausible car trajectory along the space above road (row 2).
        Row 3 and 4 show the benefit  of incorporating social factors.
        Row 3 is the visualization of vanilla LSTM: the bottom left car predictions (denoted by red dots) are considered in isolation, moving dangerously close to the two front cars.
        Row 4 is the visualization of Social-LSTM: by considering two front cars in the scene, the prediction keeps the red dot car in a safer distance from the two front cars.
        }
        }
        \label{fig:final}
\end{figure*}

@@

%%%%%%%%%%%%%%%%%
\begin{table}[t]
\small
   \centering
        %\begin{tabular}{|l *{2}{c}|}\hline
        %\begin{tabu}{|l *{2}{c}|}
        \begin{tabu}{@{}ccc@{}}\toprule
        [-1pt] \tabucline[1pt]{1-3}
                                                    &   Ave. disp. error      & Final disp. error   \\ \hline
            {\small Vanilla LSTM }                 &     0.0514              &  0.0880   \\
            {\small \textbf{Social-LSTM} }         &  \textbf{0.0494 }         & \textbf{0.0837}   \\
          [-1pt] \tabucline[1pt]{1-3}
        \end{tabu}
        %\end{tabular}

    \caption{ {\small Results comparing vanilla LSTM and Social-LSTM in  unit space. \emph{Ave. disp. error} is the mean square error over all estimated points of a trajectory and the true points. \emph{Final disp. error} is the distance beween the predicted final destination and the true final destination at the end of the prediction period $T_F$.
     }
    } \label{tab:social_lstm}
\end{table}

%\vspace{\baselineskip}
\noindent \textbf{Learning with auxiliary information:}
 The 2D and 3D evaluation results in Fig.~\ref{fig:precision_plot_and_success_plot} and Tab.~\ref{table_baseline_2d}  show that our proposed system consistently outperforms the baseline Kalman filter. Kalman filter is intrinsically a linear model and it's difficult to handle highly nonlinear driving trajectories in a relative coordinates.
 The auxiliary learning with semantic information in SEG-LSTM also consistently outperforms other two temporal models.
 Fig.~\ref{fig:final} shows the advantage of using SEG-LSTM: by utilizing the scene semantics (\emph{e.g.}, road, cars), it's able to direct the recurrent net to output the most plausible path for vehicles and avoid collision with neighboring vehicles.

%\vspace{\baselineskip}
\noindent \textbf{Learning with social tensor:}
On average, there is around 3 cars of interests in a high-way driving scene.
Tab.~\ref{tab:social_lstm} shows that considering social interactions between cars improves the prediction accuracy over the isolation case.
And we believe that in a more complex social scene such as urban driving, the improvement will be more pronounced.
